\subsection*{1.2 Target Applications}
\addcontentsline{toc}{subsection}{1.2 Target Applications}

NORA is designed as a versatile and modular embedded system suitable for a broad range of applications where localized intelligence, multimodal interaction, and deterministic behavior are required. The system’s internal modularity, open design, and local processing capabilities make it particularly well suited for the following domains:

\subsubsection*{Educational Environments}
\begin{itemize}
    \item Robotics laboratory exercises and embedded systems coursework.
    \item Training platforms for FSM design, voice interaction, and multimodal integration.
    \item Student projects in physical computing, AI, or human-machine interaction.
\end{itemize}

\subsubsection*{Research and Prototyping}
\begin{itemize}
    \item Human-aware robotics, embedded agents, and dialogue systems.
    \item On-device AI research in vision, audio, or reinforcement learning.
    \item Experimental deployments for multimodal user studies.
\end{itemize}

\subsubsection*{Personal Assistance and Home Integration}
\begin{itemize}
    \item Local smart assistant for room-level interaction.
    \item Data logger and personal memory tool with offline NAS storage.
    \item Mobile assistant for intradomestic navigation and object detection.
\end{itemize}

\subsubsection*{Interactive Installations and Public Spaces}
\begin{itemize}
    \item Kiosks or assistive robots in museums, galleries, or libraries.
    \item Demonstrators for educational fairs, exhibitions, or science outreach.
    \item Emotion-aware installations for ambient feedback or guidance.
\end{itemize}

\subsubsection*{Testbed for Advanced Control Systems}
\begin{itemize}
    \item Finite State Machine experimentation and behavior graph validation.
    \item Real-time sensor fusion using voice, image, and environmental inputs.
    \item Controlled evaluation of system transitions under dynamic conditions.
\end{itemize}

\subsubsection*{Privacy-Conscious Environments}
\begin{itemize}
    \item Use cases where no data should leave the local network.
    \item Offline interaction systems for children, patients, or vulnerable users.
    \item Regulatory environments (e.g., GDPR-restricted regions) where cloud-free operation is required.
\end{itemize}
